The Effect of a Second AIDS Defining Illness on Survival in the MACS

### 2015-05-05 paper.Rmd
First draft of practicum done

knitr::kable(coef(summary(adjusted.model)),
             caption="PH Model Adjusted for Confounders")
```

@@

```{r propensity-score}
set.seed(90210)
match.set <- MatchIt::matchit(sec.aids ~ factor(race) + 
                              age.at.aids + drug.use +
                              aids.year + depression + cd4,
                              data=time.varying,
                              distance="logit",
                              method="nearest",
                              caliper=.07,
                              discard="both")

@@

There were `r length(unique(matched.dat$STUDYID))` individuals in the 
matched data set of the orginal `r nrow(data)`. There are 
`r sum(matched.dat$sec.aids)` events in the matched data set.
We perform a check on the data and see the following summaries.

```{r}
knitr::kable(match.check$sum.all,
             caption="Summary of balance for all data")
knitr::kable(match.check$sum.matched,
             caption="Summary of balance for matched data")
knitr::kable(match.check$reduction,
             caption="Percent Balance Improvement")
knitr::kable(match.check$nn,
             caption="Sample Sizes")
```

@@

```{r}
knitr::kable(coef(summary(ph.match)),
             caption="PH Model (Propensity Scores)")
```

```{r}
# ########################################################################
# ## Q10b Get HRs after matching with higher caliper
# ########################################################################
# 
# 
# set.seed(1428)
# match2.set <- matchit(hivhrt~age + bmi,data=dat,distance=dat$cpoe,method="nearest",caliper=.5,discard="both")
# 
# ## let's check out the diagnostics
# 
# ## numerical check
# print(sum.match2 <- summary(match2.set,standardize=T))
# 
# ## graphical check
# plot(match2.set,type="jitter",interactive=F)
# plot(sum.match2,interactive=F)
# 
# matched2.dat <- match.data(match2.set,"all")
# 
# ## how many individuals in matched.dat?
# nrow(matched2.dat)
# 
# ##
# sum(matched2.dat$dm)
# 
# ph.match2 <- coxph(Surv(time=t,event=dm)~hivhrt,data=matched2.dat,method="efron")
# summary(ph.match2)
# 
# 
# 
# 
# ########################################################################
# ## Q10c Get HRs after subclassification
# ########################################################################
# 
# 
# dat$hivhrtn <- as.numeric(dat$hivhrt)-1
# sub.set <- matchit(hivhrtn~age + bmi,data=dat,method="subclass",sub.by="all",subclass=5,discard="both")
# 
# summary(sub.set,standardize=T)
# plot(sub.set,type="jitter",interactive=F)
# plot(summary(sub.set,standardize=T),interactive=F)
# 
# sub.dat <- match.data(sub.set,"all")
# ph.sub <- coxph(Surv(time=t,event=dm)~hivhrtn+strata(subclass),data=sub.dat,method="efron")
# summary(ph.sub)
```

```{r graphs}
plot(survfit(ph.match))
```

>>>>

adjusted.model.ph <- cox.zph(adjusted.model)

knitr::kable(coef(summary(adjusted.model)),
             caption="PH Model Adjusted for Confounders")

knitr::kable(cox.zph(adjusted.model)$table,
             caption="PH Assumption Test")
```

@@

```{r propensity-score}
caliper <- 0.07
set.seed(90210)
match.set <- MatchIt::matchit(sec.aids ~ factor(race) + 
                              age.at.aids + drug.use +
                              aids.year + depression + cd4,
                              data=time.varying,
                              distance="logit",
                              method="nearest",
                              caliper=caliper,
                              discard="both")

@@

There were `r length(unique(matched.dat$STUDYID))` individuals in the 
matched data set of the orginal `r nrow(data)`. There are 
`r sum(matched.dat$sec.aids)` events in the matched data set.
We perform a check on the data and see the following summaries. We used a
caliper of `r caliper`.

```{r}
knitr::kable(match.check$sum.all[,1:4],
             caption="Summary of balance for all data")
knitr::kable(match.check$sum.matched[,1:4],
             caption="Summary of balance for matched data")
knitr::kable(match.check$reduction,
             caption="Percent Balance Improvement")
knitr::kable(match.check$nn,
             caption="Sample Sizes")
```

@@

```{r}
knitr::kable(coef(summary(ph.match)),
             caption="PH Model (Propensity Scores)")

knitr::kable(cox.zph(ph.match)$table,
             caption="PH Assumption Test")
caliper <- 0.5
```

Next, we performed the same PH model using propensity scores, but with a higher
caliper (`r caliper`).

```{r propensity-score-2}
set.seed(90210)
match.set <- MatchIt::matchit(sec.aids ~ factor(race) + 
                              age.at.aids + drug.use +
                              aids.year + depression + cd4,
                              data=time.varying,
                              distance="logit",
                              method="nearest",
                              caliper=caliper,
                              discard="both")

There were `r length(unique(matched.dat$STUDYID))` individuals in the 
new matched data set of the orginal `r nrow(data)`. There are 
`r sum(matched.dat$sec.aids)` events in the matched data set.
We perform a check on the data and see the following summaries.

```{r}
knitr::kable(match.check$sum.all[,1:4],
             caption="Summary of balance for all data")
knitr::kable(match.check$sum.matched[,1:4],
             caption="Summary of balance for matched data")
knitr::kable(match.check$reduction,
             caption="Percent Balance Improvement")
knitr::kable(match.check$nn,
             caption="Sample Sizes")
```

In our second PH model with propensity scores, we see the following results.

```{r}
knitr::kable(coef(summary(ph.match)),
             caption="PH Model (Propensity Scores)")

knitr::kable(cox.zph(ph.match)$table,
             caption="PH Assumption Test")
caliper <- 0.5
```

Finally, we used a subclassification method for our propensity score.

```{r subclass}
sub.set <- MatchIt::matchit(sec.aids ~ factor(race) + 
                            age.at.aids + drug.use +
                            aids.year + depression + cd4,
                            data=time.varying,
                            method="subclass",
                            sub.by="all",
                            subclass=5)

# summary(sub.set,standardize=T)
plot(sub.set,type="jitter",interactive=F)
# plot(summary(sub.set,standardize=T),interactive=F)

sub.dat <- MatchIt::match.data(sub.set, "all")
ph.match <- coxph(Surv(start, stop, status) ~ sec.aids + strata(subclass),
   				  data=sub.dat,
                  method="efron")
knitr::kable(coef(summary(ph.match)),
             caption="PH Model (Propensity Scores)")

knitr::kable(cox.zph(ph.match)$table,
             caption="PH Assumption Test")
```

```{r graphs}
plot(survfit(ph.match), main="Final PH Model Using Subclassification")
```
